### 2018-12-10 Paper/revision/source_files/intro.tex
..

The contributions of this article are as follows: (i) We establish a robust and
practical framework for dimension reduction and surrogate modeling using
derivative-based global sensitivity measures. Our
approach is general in that it is applicable to a wide range of applications.
(ii) We present comprehensive numerical results demonstrating the viability of
our strategy using motivating applications: the classic borehole
function, and a semilinear elliptic PDE.  (iii) We 
deploy our strategy in an application problem from chemical kinetics with 19
uncertain rate-controlling parameters. The problem is studied in multiple regimes.
It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
or 4-dimensional problem. \rebut{The strategy is further implemented to a
higher dimensional problem involving 33 uncertain rate-controlling parameters.
In this case, it is shown that only 2 out of 33 parameters predominantly 
contribute to the uncertainty in the quantity of interest (QoI). Moreover, 
computational gains using the proposed strategy are shown to increase significantly
with dimensionality.}

>>>>

The contributions of this article are as follows: (i) We establish a robust and
practical framework for dimension reduction and surrogate modeling using
derivative-based global sensitivity measures. Our
approach is general in that it is applicable to a wide range of applications.
(ii) We present comprehensive numerical results demonstrating the viability of
our strategy using motivating applications: the classic borehole
function, and a semilinear elliptic PDE.  (iii) We 
deploy our strategy in an application problem from chemical kinetics with 19
uncertain rate-controlling parameters. The problem is studied in multiple regimes.
It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
or 4-dimensional problem. The strategy is further implemented to a
higher dimensional problem involving 33 uncertain rate-controlling parameters.
In this case, it is shown that only 2 out of 33 parameters predominantly 
contribute to the uncertainty in the quantity of interest (QoI). Moreover, 
computational gains using the proposed strategy are shown to increase significantly
with dimensionality.
